A Classical Density-Functional Theory for Describing Water Interfaces

### 2011-12-07 paper/paper.tex
various changes on sphere in water Tested everything.

We use a free square-well function for the dispersion $\varphi$, which
is the choice used by Clark \emph{et al}~\cite{clark2006developing},
and allows a reasonable fit to the equation of state.  Thus our model
interaction has the form:
\begin{equation}
  \varphi(r) = \color{red}\Theta(r-2 \lambdadisp R)
\end{equation}
where $\Theta$ is the Heaviside step function.

The form of $a_1$ is given in
reference~\cite{gil-villegas-1997-SAFT-VR}, but is expressed in terms
of the filling fraction.  In order to apply this form to an
inhomogeneous density distribution, we construct an effective local
filling fraction for dispersion $\etadisp$, given by
\begin{align}
  \etadisp(\xx) &=
  \int \frac{\Theta(2\lambdadisp\lscale R - \left|\xx-\xx'\right|)}{
             \left(2\lambdadisp\lscale\right)^3} n(\xx') d\xx'.
\end{align}
This effective filling fraction is used throughout the dispersion
calculations, and represents a filling fraction averaged over the
effective range of the dispersive interaction.  This functional
introduces an additional empirical parameter $\lscale$ which adjusts
the length scale over which the dispersion interaction is correlated.

@@

\begin{figure}[b]
\begin{center}
%\includegraphics[width=\columnwidth]{radial-plots/cavity-density}
\end{center}
\caption{Density profiles for multiple sizes of hard sphere solute.
  Results from a simulation of SPC/E water~\cite{huang2001shs} are
  shown as a dotted lines.}
\label{fig:cavities}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figs/sphere-energy-vs-diameter}
\end{center}
\caption{ Free energy versus radius for a single hydrophobic sphere
immersed in water. This should have an asymptote equal to the surface
tension at room temperature, and it agrees well with the surface tension in
Figure~\ref{fig:surface-tension}. }
\label{fig:sphere-energy-vs-diameter}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figs/density-sphere}
\end{center}
\caption{ Density profiles for spheres of different radii. The dotted line
represents the saturated liquid density.  }
\label{fig:density-sphere}
\end{figure}

>>>>

We use a free square-well function for the dispersion $\varphi$, which
is the choice used by Clark \emph{et al}~\cite{clark2006developing},
and allows a reasonable fit to the equation of state.  Thus our model
interaction has the form:
\begin{equation}
  \varphi(r) = \Theta(r-2 \lambdadisp R)
\end{equation}
where $\Theta$ is the Heaviside step function.

The form of $a_1$ is given in
reference~\cite{gil-villegas-1997-SAFT-VR}, but is expressed in terms
of the filling fraction.  In order to apply this form to an
inhomogeneous density distribution, we construct an effective local
filling fraction for dispersion $\etadisp$, given by
\begin{align}
%    ((4/3.0*M_PI)*Pow(3)(R)*GaussianConvolve(2*lambdainput*lscale*radius,
%                                             2*lambdaE*length_scalingE*Rexpr)
%  \etadisp(\xx) &= \color{red}
%  \int \frac{\Theta(2\lambdadisp\lscale R - \left|\xx-\xx'\right|)}{
%             \left(2\lambdadisp\lscale\right)^3} n(\xx') d\xx'.
  \\
  \etadisp(\xx) &= \frac{1}{6\sqrt{\pi} \lambdadisp^3\lscale^3}
  \int n(\xx')\exp\left({-\frac{|\xx-\xx'|^2}{2(2 \lambdadisp
      \lscale R)^2}}\right)d\xx'
\end{align}
This effective filling fraction is used throughout the dispersion
calculations, and represents a filling fraction averaged over the
effective range of the dispersive interaction.  This functional
introduces an additional empirical parameter $\lscale$ which adjusts
the length scale over which the dispersion interaction is correlated.

@@

\begin{figure}[b]
\begin{center}
%\includegraphics[width=\columnwidth]{radial-plots/cavity-density}
\end{center}
\caption{Density profiles for multiple sizes of hard sphere solute.
  }
\label{fig:cavities}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figs/sphere-energy-vs-diameter}
\end{center}
\caption{ Free energy versus radius for a single hydrophobic sphere
  immersed in water. This should have an asymptote equal to the
  surface tension at room temperature, and it agrees well with the
  surface tension in Figure~\ref{fig:surface-tension}. Results from a
  simulation of SPC/E water~\cite{huang2001shs} are shown as
  circles. }
\label{fig:sphere-energy-vs-diameter}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figs/density-sphere}
\end{center}
\caption{ Density profiles around hard-sphere solutes of different radii. Predictions
  from our classical density-functional theory are in solid red, while
  the dotted line shows the result of a molecular dynamics simulation
  of SPC/E water~\cite{huang2001shs}.  }
\label{fig:density-sphere}
\end{figure}
